---
title: "Reproducible Research : Peer Assessment 1"
output: html_document
---
Load the data

```{r}
activity <- read.csv("activity.csv",colClasses =c("numeric","character","numeric"))
head(activity)
names(activity)
#library(lattice)
#activity$date <- as.Date(activity$date,"%Y-%m-%d")
```
####What is mean total number of steps taken per day?
1.Calculate the total number of steps taken per day
```{r}

total.steps <- tapply(activity$steps,activity$date,FUN=sum,na.rm=TRUE)
print(total.steps)
```
2.Histogram of the total number of steps taken each day
```{r}
library(ggplot2)
qplot(total.steps,binwidth=500,xlab="Total no.steps per day")
```


3.Calculate and report the mean and median of the total number of steps taken per day
```{r}
print("Mean of the total number steps /day")
mean.total <- mean(total.steps,na.rm = TRUE)
print(mean.total)
print("Median of the total number steps /day")
median.total <- median(total.steps,na.rm = TRUE)
print(median.total)

```

####What is the average daily activity pattern?
1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
avg <- aggregate(x=list(steps=activity$steps),by=list(interval=activity$interval),FUN=mean,na.rm=TRUE)
#ggplot(data=avg,aes(x=interval,y=steps)) #+geom_line(aes(group=1),colour="#000099") +xlab("Five minute Interval") + #ylab("Avg no. of steps taken")
ggplot(data=avg,aes(x=interval,y=steps))  +xlab("Five minute Interval") + ylab("Avg no. of steps taken") +geom_line(aes(group=1),colour="#000099") +
geom_point(size=1,colour="#CC0000")
```


2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
print("Max no. of steps")
avg[which.max(avg$steps),]

```
####Imputing missing values
1.Calculate and report the total number of missing values in the dataset 
```{r}
missing <- sum(is.na(activity$steps))
print(missing)
```

2.Devise a strategy for filling in all of the missing values in the dataset. 
```{r}
#Missing value will be replaced by mean in 5 min interval
fill.missvalue <- function(steps,interval){
  filled <- NA
  if(!is.na(steps))
    filled <-c(steps) 
  else 
    filled <- (avg[avg$interval == interval,"steps"])
  return(filled)
}
filled.activity <-activity
filled.activity$steps <- mapply(fill.missvalue,filled.activity$steps,filled.activity$interval)
```


3. Create a new dataset that is equal to the original dataset but with the missing data filled in.


```{r}
total.steps <- tapply(filled.activity$steps,filled.activity$date,FUN=sum)

```


4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?
```{r}
qplot(total.steps,binwdth=500)

mean(total.steps)

median(total.steps)
```
